Enriching Object Detection with 2D-3D Registration and Continuous Viewpoint

### 2014-11-14 approach.tex
redstuff
spellcheck exp
spell check approach

\begin{figure}[t]
  \begin{center}
     \includegraphics[width=0.4\linewidth]{rendering}
     \includegraphics[width=0.4\linewidth]{depth}
  \end{center}
  \caption{An example rendering and depth image made by our renderer}
  \label{fig:rendering}
\end{figure}

@@

Whitening the non-zero
feature vector $x'$ means a solving the system of linear equations, $\Sigma' w' = (x' -
\mu')$. In
\cite{Hariharan12}, the authors make use of the fact that covariance matrices
are symmetric and positive semidefinite to solve the system via the Cholesky
decomposition with Gaussian Elemination, which requires $O(n^3)$ time \scream{Citation for complexity}.

The Conjugate Gradient method is an iterative algorithm for solving symmetric
positive definite systems which runs in $O(n^2\kappa)$ time, where $\kappa$ is
the condition number of the matrix. \scream{Citation for complexity}.
%
This makes Conjugate Gradient faster than decomposition for matrices with small condition
numbers relative to their size.

@@

As a result, a GPU implementation of conjugate gradient converges in 50
ms when using 250 HOG cells, two orders of magnitude faster than the using
Cholesky factorization with Gaussian Elemination.

@@

In addition, since the iterative Conjugate Gradient method directly
tries to reduce the residual (the norm of $y-Ax$ for $Ax = y$), it is
more numerically stable than Cholesky decomposition with Gaussian
Elemination. We vary the number of cells in a template and show that
the residual of NZ-WHO is smaller than WHO Fig.~\ref{fig:whoresidual}.
% Also, the residual from the Conjugate Gradient method (the norm of $y-Ax$ for $Ax = y$) is smaller than 
% that of Cholesky decomposition.

>>>>

\begin{figure}[t]
  \begin{center}
     \includegraphics[width=0.4\linewidth]{rendering}
     \includegraphics[width=0.4\linewidth]{depth}
  \end{center}
  \caption{An example rendering and depth image from renderer.}
  \label{fig:rendering}
\end{figure}

@@

Whitening the non-zero
feature vector $x'$ means a solving the system of linear equations, $\Sigma' w' = (x' -
\mu')$. In
\cite{Hariharan12}, the authors make use of the fact that covariance matrices
are symmetric and positive semidefinite to solve the system via the Cholesky
decomposition with Gaussian Elimination, which requires $O(n^3)$ time \scream{Citation for complexity}.

The Conjugate Gradient method is an iterative algorithm for solving symmetric
positive definite systems which runs in $O(n^2\kappa)$ time, where $\kappa$ is
the condition number of the matrix. \cite{Shewchuk94}.
%
This makes Conjugate Gradient faster than decomposition for matrices with small condition
numbers relative to their size.

@@

As a result, a GPU implementation of conjugate gradient converges in 50
ms when using 250 HOG cells, two orders of magnitude faster than the using
Cholesky factorization with Gaussian Elimination.

@@

In addition, since the iterative Conjugate Gradient method directly
tries to reduce the residual (the norm of $y-Ax$ for $Ax = y$), it is
more numerically stable than Cholesky decomposition with Gaussian
Elimination. We vary the number of cells in a template and show that
the residual of NZ-WHO is smaller than WHO Fig.~\ref{fig:whoresidual}.
% Also, the residual from the Conjugate Gradient method (the norm of $y-Ax$ for $Ax = y$) is smaller than 
% that of Cholesky decomposition.
